Effects of sexual selection on non-sexual fitness components: a meta-analysis

### 2018-05-04 meta_analysis_sexual_selection_pop_fitness.Rmd
4/5 update

# svg("figures/Big_forest_plot.svg", width=12, height=18)
# p.meta
# dev.off()
```
<br></br>
**Figure S1:** Forest plot of raw effect sizes and their 95% confidence intervals, grouped according to environment (stressed or unstressed) and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together). Rows with multiple data points denote studies that provided multiple effect sizes. Positive values indicate fitness benefits of sexual selection.

@@

outcome.frame <- format(simple.frame, digits = 2)
outcome.frame <- add_rownames(outcome.frame, "Outcome")
outcome.frame$b <- as.numeric(outcome.frame$b)
outcome.frame$k <- as.numeric(outcome.frame$k)
outcome.frame$ci.lb <- as.numeric(outcome.frame$ci.lb)
outcome.frame$ci.ub <- as.numeric(outcome.frame$ci.ub)
outcome.frame$I2 <- as.numeric(outcome.frame$I2)

@@

**Table S8**
```{r}
colnames(predictions.complete2) <- c("Sex", "Environment", "Prediction", "SE", "CI.lb", "CI.ub", "n")
predictions.complete2 <- format(predictions.complete2, digits = 2)
predictions.complete2 %>% pander()
```

@@

```{r}
anova(model.complete2, L=c(0, 1, 0, -1, 0, 0)) 
```

@@

We can also test if there is a difference between males and females in unstressed and stressed conditions:

>>>>

# svg("figures/Big_forest_plot.svg", width=12, height=18)
# p.meta
# dev.off()
```
<br></br>
**Figure S1:** Forest plot of raw effect sizes and their 95% confidence intervals, grouped according to measured fitness components and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together). Rows with multiple data points denote studies that provided multiple effect sizes. Positive values indicate fitness benefits of sexual selection.

@@

outcome.frame <- format(simple.frame, digits = 2)
outcome.frame <- add_rownames(outcome.frame, "Outcome")
outcome.frame$b <- as.numeric(outcome.frame$b)
outcome.frame$k <- as.numeric(outcome.frame$k)
outcome.frame$ci.lb <- as.numeric(outcome.frame$ci.lb)
outcome.frame$ci.ub <- as.numeric(outcome.frame$ci.ub)
outcome.frame$I2 <- as.numeric(outcome.frame$I2)
outcome.frame$Class <- c("Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Direct", "Direct", "Direct")

@@

**Table S8** The predictions in the plot above use the following dataframe
```{r}
colnames(predictions.complete2) <- c("Sex", "Environment", "Prediction", "SE", "CI.lb", "CI.ub", "n")
predictions.complete2 <- format(predictions.complete2, digits = 2)
predictions.complete2 %>% pander()
```

@@

Both (unstressed vs stressed)
```{r}
anova(model.complete2, L=c(0, 1, 0, -1, 0, 0)) 
```

@@

We can also test if there is a difference between males and females in unstressed conditions:
